---
title: "Activity 2 - Day 1"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Task 2: Loading required Packages
```{r}
# Loading required packages
library(tidyverse)
library(tidymodels)
library(ggplot2)
```

## Task 3: Reading the dataset from URL

```{r}
hfi <- readr::read_csv("https://www.openintro.org/data/csv/hfi.csv")

hfi
```
1) From the dataset I could find that dimensions are **1458 X 123**. Each row represents data for each country.

```{r}
hfi_2016 <- hfi %>% filter(year == 2016)

hfi_2016
```

2) These two columns **pf_score** and **pf_expression_control** are the numerical variables. However, in my opinion in order find the relation between these columns _Scatter Plot_ will be one of the suitable plot.

```{r}
ggplot(data = hfi_2016, aes(y = pf_score, x = pf_expression_control)) +
  geom_point()
```
3) I can see that this scatter plot is _Linearly Plotted_



## Task 4: Sum of squared residuals


```{r}
statsr::plot_ss(x = pf_expression_control, y = pf_score, data = hfi_2016)
```

## Task 5: Linear Model

```{r}
m1 <- lm(pf_score ~ pf_expression_control, data = hfi_2016)

tidy(m1)
```
5. Intercept of Y-intercept is **4.28**
6. Intercept of slope is **0.542**


# Day 2 >> __Assessing an SLR Model__

## Task -1 

Successfully pulled the data from the repo.

## Task 2 
```{r}
cor(hfi_2016$pf_expression_control,hfi_2016$pf_score)
```

1. I have received the correlation coefficient is `r cor(hfi_2016$pf_expression_control,hfi_2016$pf_score)`. As the value is more than zero, we can say that it has a significantly positive relation between these two variables.



```{r}
glance(m1)
```
2. r^2 value is 0.714 

3. It defines that more of the observation has been explained in the model's input.

```{r}
m2 <- lm(pf_score ~ hf_score, data = hfi_2016)

tidy(m2)
```

The equation which I can represent from the above values is $y = -2.027077 + 1.30 * hf_score$

```{r}
ggplot(data = hfi_2016, aes(y = pf_score, x = hf_score)) +
  geom_point()+
  geom_smooth(method = lm)+
  labs(title = " Linear method for pf_score and hf_score",
       x= "hf_score",
       y= "pf_score")
```
## Task 4 - Model Diagnostics 

```{r}
m1_aug <- augment(m1)
```

```{r}
ggplot(data = m1_aug, aes(x = .fitted, y = .resid)) +
  geom_point() +
  geom_hline(yintercept = 0, linetype = "dashed", color = "red") +
  xlab("Fitted values") +
  ylab("Residuals")
```
From my understanding from the above plot I can see that points are scatter all around which doesn't defines any pattern. By this I can say that the plot is linearly appropriate model.


```{r}
ggplot(data = m1_aug, aes(x = .resid)) +
  geom_histogram(binwidth = 0.25) +
  xlab("Residuals")
```

